---
title: "Hotel reviews for git"
author: "Lukas"
date: "September 11, 2019"
output: 
  html_document:
    keep_md: true
---
```{r setup, include=FALSE, warning = F}
knitr::opts_chunk$set(echo = TRUE)
```

#Introduction
This projects includes data preprocessing and some vizualisations about hotels across Europe. Dataset contains 515,000 customer reviews of 1493 luxury hotels. 

#Preparations {.tabset .tabset-fade .tabset-pills}

##Loading libraries
Libraries that will be used for project:
```{r, message=FALSE, warning=FALSE, results='hide'}
library(dplyr) 
library(ggplot2)
library(stringr)
library(tm) 
library(wordcloud) 
library(leaflet) 
library(mapview) 
library(data.table)
```

##Reading data
```{r, message=FALSE, warning=FALSE, results='hide'}
path2 <- "C:/Users/Lukas/Desktop/R2/Hotel Reviews/Input/Hotel_Reviews.csv"
data <- fread(path2, header = TRUE, showProgress = FALSE)
```

```{r, include=FALSE}
options(tibble.width = Inf)
```

#Exploring data{.tabset}

##Dimensions
```{r, results='asis'}
cat("Number of observations in dataset:", dim(data)[1],", number of features:", dim(data)[2])
```

##Structure
```{r, tidy = TRUE}
str(data)
```

##Summary
```{r, tidy = TRUE}
summary(data)
```

##Missing values
Dataset contains 6536 missing values.
```{r, tidy = TRUE}
cat("Number of missing values in dataset:",  sum(is.na(data)))
```
##

Extracting columns with missing values.
```{r}
missing_values <- lapply(data,function(x) sum(is.na(x)))
missing_values[missing_values>0]
```

Number of hotels with missing values in latitude and longitude:
```{r}
table_with_missing_values <- data[which(is.na(data$lat == TRUE)), ] 
length(unique(table_with_missing_values$Hotel_Address))
```

Hotel names with missing values:
```{r}
unique(table_with_missing_values$Hotel_Address)
```

Removing duplicates from data
```{r}
data <- distinct(data)
```

Filling missing values manually with cordinates from the internet
```{r, results='hide'}
data[data$Hotel_Address == "20 Rue De La Ga t 14th arr 75014 Paris France", ncol(data)] <- 2.323509
data[data$Hotel_Address == "20 Rue De La Ga t 14th arr 75014 Paris France", ncol(data)-1] <- 48.840747
data[data$Hotel_Address == "4 rue de la P pini re 8th arr 75008 Paris France", ncol(data)] <- 2.322156
data[data$Hotel_Address == "4 rue de la P pini re 8th arr 75008 Paris France", ncol(data)-1] <- 48.875382
data[data$Hotel_Address == "Gr nentorgasse 30 09 Alsergrund 1090 Vienna Austria", ncol(data)] <- 16.356793
data[data$Hotel_Address == "Gr nentorgasse 30 09 Alsergrund 1090 Vienna Austria", ncol(data)-1] <- 48.224874
data[data$Hotel_Address == "Josefst dter Stra e 10 12 08 Josefstadt 1080 Vienna Austria", ncol(data)] <- 16.353097
data[data$Hotel_Address == "Josefst dter Stra e 10 12 08 Josefstadt 1080 Vienna Austria", ncol(data)-1] <- 48.209445
data[data$Hotel_Address == "Landstra er G rtel 5 03 Landstra e 1030 Vienna Austria", ncol(data)] <- 16.393673
data[data$Hotel_Address == "Landstra er G rtel 5 03 Landstra e 1030 Vienna Austria", ncol(data)-1] <- 48.211162
data[data$Hotel_Address == "Pau Clar s 122 Eixample 08009 Barcelona Spain", ncol(data)] <- 2.170299
data[data$Hotel_Address == "Pau Clar s 122 Eixample 08009 Barcelona Spain", ncol(data)-1] <- 41.394611
data[data$Hotel_Address == "Sep lveda 180 Eixample 08011 Barcelona Spain", ncol(data)] <- 2.160687
data[data$Hotel_Address == "Sep lveda 180 Eixample 08011 Barcelona Spain", ncol(data)-1] <- 41.384845
data[data$Hotel_Address == "Taborstra e 8 A 02 Leopoldstadt 1020 Vienna Austria", ncol(data)] <- 16.414759
data[data$Hotel_Address == "Taborstra e 8 A 02 Leopoldstadt 1020 Vienna Austria", ncol(data)-1] <- 48.209254
data[data$Hotel_Address == "W hringer Stra e 33 35 09 Alsergrund 1090 Vienna Austria", ncol(data)] <- 16.356514
data[data$Hotel_Address == "W hringer Stra e 33 35 09 Alsergrund 1090 Vienna Austria", ncol(data)-1] <- 48.224946
data[data$Hotel_Address == "23 Rue Damr mont 18th arr 75018 Paris France", ncol(data)] <- 2.342705
data[data$Hotel_Address == "23 Rue Damr mont 18th arr 75018 Paris France", ncol(data)-1] <- 48.888148
data[data$Hotel_Address == "Bail n 4 6 Eixample 08010 Barcelona Spain", ncol(data)] <- 2.177693
data[data$Hotel_Address == "Bail n 4 6 Eixample 08010 Barcelona Spain", ncol(data)-1] <- 41.391972
data[data$Hotel_Address == "Hasenauerstra e 12 19 D bling 1190 Vienna Austria", ncol(data)] <- 16.345239
data[data$Hotel_Address == "Hasenauerstra e 12 19 D bling 1190 Vienna Austria", ncol(data)-1] <- 48.233705
data[data$Hotel_Address == "Josefst dter Stra e 22 08 Josefstadt 1080 Vienna Austria", ncol(data)] <- 16.351014
data[data$Hotel_Address == "Josefst dter Stra e 22 08 Josefstadt 1080 Vienna Austria", ncol(data)-1] <- 48.209659
data[data$Hotel_Address == "Paragonstra e 1 11 Simmering 1110 Vienna Austria", ncol(data)] <- 16.418367
data[data$Hotel_Address == "Paragonstra e 1 11 Simmering 1110 Vienna Austria", ncol(data)-1] <- 48.171124
data[data$Hotel_Address == "Savoyenstra e 2 16 Ottakring 1160 Vienna Austria", ncol(data)] <- 16.302941
data[data$Hotel_Address == "Savoyenstra e 2 16 Ottakring 1160 Vienna Austria", ncol(data)-1] <- 48.215164
data[data$Hotel_Address == "Sieveringer Stra e 4 19 D bling 1190 Vienna Austria", ncol(data)] <- 16.341607
data[data$Hotel_Address == "Sieveringer Stra e 4 19 D bling 1190 Vienna Austria", ncol(data)-1] <- 48.245945
data[data$Hotel_Address == "W hringer Stra e 12 09 Alsergrund 1090 Vienna Austria", ncol(data)] <- 16.359787
data[data$Hotel_Address == "W hringer Stra e 12 09 Alsergrund 1090 Vienna Austria", ncol(data)-1] <- 48.216853

```

#Data analysis
##Descriptive statistics and visualizations
Average Review Scores:
```{r}
data%>%select(Average_Score,Hotel_Address)%>%distinct(Average_Score,Hotel_Address)%>%
  ggplot(aes(x=Average_Score))+
  geom_histogram(color='black',fill='brown', bins=30)+xlab("Average Review Score") + ylab("Frequency") +
  scale_x_continuous(breaks = seq(5,10,0.5))
```

The most frequent scores:
```{r}
ggplot(data = data, aes(x = data$Reviewer_Score)) +
  geom_histogram(bins = 40, fill = "palegreen4", color='black') +
  scale_x_continuous(breaks = seq(min(data$Reviewer_Score), max(data$Reviewer_Score), 0.5)) + 
  scale_y_continuous(breaks = seq(0,120000,20000)) +
  xlab("Reviewer Score") + ylab("Frequency") +
  ggtitle("Reviewer Score Frequency") +  
  theme(plot.title = element_text(hjust = 0.5))
```

Nationalities of the people that wrote a review about hotel
```{r}
data %>% select(Reviewer_Nationality) %>% group_by(Reviewer_Nationality) %>% 
  count() %>% arrange(desc(n)) %>% head(10)
```

The most reviewed hotels:
```{r}
data %>% select(Hotel_Name, Total_Number_of_Reviews) %>% 
  arrange(desc(Total_Number_of_Reviews)) %>% distinct() %>%
  head(10) %>% select(Hotel_Name)
```

Number of total reviews reviewer has given:
```{r}
data %>% select(Total_Number_of_Reviews_Reviewer_Has_Given, Reviewer_Nationality) %>%
  group_by(Total_Number_of_Reviews_Reviewer_Has_Given) %>%
  count() %>% head(10) %>%
  ggplot(., aes(Total_Number_of_Reviews_Reviewer_Has_Given, n)) +
  geom_bar(stat = "identity", fill = "blue", color='black') + ylab("Frequency") + xlab("Total number of reviews reviewer has given") +
  ggtitle("Total number of reviews") +
  scale_x_continuous(breaks = seq_len(10))
```

Correlation coeficient between reviewer score and number of negative words in review:
```{r}
cor(data$Reviewer_Score, data$Review_Total_Negative_Word_Counts)
```

Best rated hotels: (hotels that have more than 10 reviews)
```{r}
data %>% select(Hotel_Name, Reviewer_Score) %>% group_by(Hotel_Name) %>% 
  mutate(Daznis = n()) %>% filter(Daznis > 10) %>%
  summarize(Vertinimas = mean(Reviewer_Score)) %>%
  arrange(desc(Vertinimas)) %>% head(10)
```

Worst rated hotels: (hotels that have more than 10 reviews)
```{r}
data %>% select(Hotel_Name, Reviewer_Score) %>% group_by(Hotel_Name) %>% 
  mutate(Daznis = n()) %>% filter(Daznis > 10) %>%
  summarize(Vertinimas = mean(Reviewer_Score)) %>%
  arrange((Vertinimas)) %>% head(10)
```

Dates with the biggest number of reviews written:
```{r}
data %>% select(Review_Date) %>% group_by(Review_Date) %>%
  count() %>% arrange(desc(n)) %>% head(10) %>% 
  ggplot(., aes(x = Review_Date, y = n)) +
  geom_bar(stat="identity", fill = "palegreen4", color='black') + ylab("Frequency") + 
  ggtitle("Dates with the biggest review frequences") + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

Months with a biggest number of reviews written:
```{r}
month <- sapply(data$Review_Date, function(x) as.numeric(str_split(as.character(x), "/")[[1]][1]))
month %>% as.data.frame %>% 
  ggplot(., aes(.)) +
  geom_bar(fill = "lightsalmon1") + 
  scale_x_continuous(breaks = seq_len(12)) + 
  xlab("Month") + ylab("Frequency") +
  ggtitle("Review date frequency in months") + 
  theme(plot.title = element_text(hjust = 0.5))
```

Most popular hotels for lithuanians and mean of of the score that was given:
```{r}
data %>% select(Reviewer_Nationality, Hotel_Name, Reviewer_Score) %>% 
  filter(trimws(Reviewer_Nationality) == "Lithuania") %>% 
  group_by(Hotel_Name) %>% 
  summarise(Frequency = n(), Mean = mean(Reviewer_Score)) %>%
  arrange(desc(Frequency)) %>%
  head(10)
```

Number of total reviews reviewer from Lithuania has given:
```{r}
data %>% filter(trimws(Reviewer_Nationality) == "Lithuania") %>%
  select(Total_Number_of_Reviews_Reviewer_Has_Given) %>%
  group_by(Total_Number_of_Reviews_Reviewer_Has_Given) %>% 
  count() %>% head(10) %>%
  ggplot(., aes(Total_Number_of_Reviews_Reviewer_Has_Given, n)) + 
  geom_bar(stat = "identity", fill = "palegreen4", color='green') + ylab("Frequency") + xlab("Total number of reviews reviewer from LT has given")+
  scale_x_continuous(breaks = seq_len(10))
```
 
##Wordcloud 

Preparing data for wordcloud:
```{r, warning = F}
liet <- data %>% 
  select(Reviewer_Nationality, Positive_Review, Negative_Review) %>%
  filter(trimws(Reviewer_Nationality) == "Lithuania")
liet2 <- liet[liet$Positive_Review != "No Positive" &
                liet$Negative_Review != "No Negative", ]
```

The most frequent postive words that people from LT have written in the review:
```{r, warning = F}
pos2 <- Corpus(VectorSource(liet2$Positive_Review))
pos2 <- tm_map(pos2, content_transformer(tolower))
pos2 <- tm_map(pos2, removeNumbers)          
pos2 <- tm_map(pos2, removeWords, stopwords("en"))  
pos2 <- tm_map(pos2, stripWhitespace)
tdm <- TermDocumentMatrix(pos2)
m <- as.matrix(tdm)
v <- sort(rowSums(m), decreasing = TRUE)
d <- data.frame(word = names(v), freq = v)
wordcloud(d$word, d$freq, random.order = FALSE, rot.per = 0.3, max.words = 200, colors = brewer.pal(7, "Dark2"))
```

The most frequent negative words that people from LT have written in the review:
```{r, warning = F}
neg <- Corpus(VectorSource(liet2$Negative_Review))
neg <- tm_map(neg, content_transformer(tolower))
neg <- tm_map(neg, removeNumbers)          
neg <- tm_map(neg, removeWords, stopwords("en"))  
neg <- tm_map(neg, stripWhitespace)
tdm2 <- TermDocumentMatrix(neg)
m2 <- as.matrix(tdm2)
v2 <- sort(rowSums(m2), decreasing = TRUE)
d2 <- data.frame(word = names(v2), freq = v2)
wordcloud(d2$word, d2$freq, random.order = FALSE, rot.per = 0.3, max.words = 200, colors = brewer.pal(8, "Accent"))
```

##Location of the hotels

```{r}
zem <- data %>% select(Hotel_Name, lat, lng, Average_Score) %>% distinct()
koor <- cbind(zem$lng, zem$lat)
c <- leaflet() %>% 
  addProviderTiles('OpenStreetMap.Mapnik') %>%
  addMarkers(data = koor,
             popup = paste0("Hotel: ", zem$Hotel_Name,
                          "<br>Average score: ", zem$Average_Score))
c
```

